\chapter{Overall Description}
\label{chap:overall_description}%

\section{Product Perspective}
\label{sec:product_perspective}%

\subsection{Scenarios}
\label{sub:scenarios}%

\par{\textbf{Scenario 1: ST Login and CV Upload}} Walter W. is a chemical engineering student that wants to take part
in an internship to gain more experience and insight into the field before his graduation. Having heard of S\&C he
decides to give it a shot. First, he opens the S\&C website, where he clicks on the "Student Login" button. He is
prompted to enter his university-provided email and — after that — the platform redirects him to the SSO portal of this
institution (e.g., OpenID/OAuth…) where Walter can grant S\&C the permission to retrieve his information
(name, surname, birthdate, …) directly from his school. As soon as he grants our platform the required privileges, the
user is redirected to S\&C and his profile is created successfully. Now Walter has joined S\&C successfully, but he needs
to upload his CV; to do so he goes to the "My Profile" section where he can find the "My CV" subsection. Here, the user
can load his CV by uploading a PDF — preferably in a standard format (e.g., Europass, …) — version of it. Once uploaded,
the CV is indexed, and Walter can see a bullet list of possible improvements that he can make. The user is free to fix
his CV and re-upload an updated version iteratively once he is satisfied.

\par{\textbf{Scenario 2: ST Recruitment}} Saul G. is a freshly graduated law student, before starting his doctorate
he wants to gain some work experience before his research project starts. He joined S\&C but never found anything of his
linking; one day he receives an email from our platform regarding a possible internship: it is a law firm B.C.S. S.p.A.
looking for some intern to offload some work. Saul clicks on the link in the email and sees the internship details;
interested, the user clicks on "Apply." Some days later, Saul receives another email: it is S\&C informing him that the
company is interested in his profile and wants him to compile a survey to know him better. The user clicks on the link
and fills out the requested form. A week later, Saul receives a phone call from a lawyer, Kim, informing him that they
will work together: HR has found Saul as the idea candidate for the internship. During all the time of the selection
the user could see the internship status (when he has applied, if there are some forms to submit, …) from the
"My Internship" section so that no information is lost in case of accidental email deletion. Unread messages from S\&C
to the user can be seen on the "My Notification" section.

\par{\textbf{Scenario 3: ST Sends a Feedback on the Internship}} Marie S. is an intern at a pharmaceutical company,
and she is starting to feel mistreated in her workplace: her boss yells at her for no reason all the time and she is
forced to do work outside what she agreed on. Marie goes to S\&C, finds her internship in the "My Internship" section
and clicks on "Submit feedback" and describes the situation. The next day, Marie receives a phone call from her
university: the internship is cancelled, and appropriate actions will be taken against the corporation. The change in
the internship status is also visible in S\&C.

\par{\textbf{Scenario 4: CO Registration}} Tim I. is the CEO of a telecom company, TLC S.p.A. Having heard the
complaints from his VP of HR regarding the urgency of new workers, decides to enroll his company to S\&C hoping to find
skillful interns to then hire into the workforce. After a negotiation with the platform sales department, they agreed
to a fair contract between the parties. Then, a set of credentials is created to be used by an HR referent
– Tyrell W. — in TCL S.p.A.

\par{\textbf{Scenario 5: CO Publishes an Internship}} Tyrell W. — the HR referent for S\&C in TCL S.p.A. — log onto the
platform, using the "Company login" button, for the first time with the provided credentials. He is asked to build the
company’s profile on the platform by providing all necessary information (e.g., logo, mission, …); this profile will be
seen by the students that clicks on the company name on the various internship’s ads. The user now can go to the
"My Internship" section where he can create a new job posting; after all necessary information is provided the listing
is scanned and indexed. The company can see some suggestions on how to improve the ads copy: Tyrell is free to
iteratively adjust the ads until he is satisfied with the result.

\par{\textbf{Scenario 6: CO Recruitment}} After the registration deadline – having lots of applicants - Tyrell decides
to ask the students to fill out a questionnaire. He could have chosen to send it to a specific subset of applicants
– therefore rejecting students in the first phase of the recruitment process - but he decided to submit it to all of
them. S\&C automatically evaluates the response given by the students using the criteria provided by the company. After
the submission deadline Tyrell looks at the top 20 CV – ranked by the points gained in the questionnaire – and choose
the ten students to hire rejecting the unfit candidates. If Tyrell wanted, S\&C had recommended him directly some CVs
of students that were considered a good fit for the internship. These curricula were available in the "My Internship"
section and were properly anonymized to prevent any kind of bias. Tyrell, if he wanted, could have asked these students
to apply for the internship therefore increasing the number of total applicants. S\&C would have taken care of
notifying the students of the company's interest but the final decision on applying was left to the students.

\par{\textbf{Scenario 7: CO Sends a Feedback on the Internship}} During the internship, the students were tasked with
creating the engine that – given an address – returns the services TLC can offer at that location. The students,
however, failed in doing such: the tool-built returns lots of covered locations as unreachable by TCL network causing
serious economic damage for the company. Tyrell decides to go the "My Internship" section and send feedback to the
university. The next day the university calls TLC: the internship is suspended and the students fired.

\par{\textbf{Scenario 8: UN Registration}} PoliPo – Polytechnic University of Pordenone – is a well-known Italian
university. Their rector has decided that they are going to join S\&C to allow their students to gain some work
experience and to boost the "student employability" ranking of the university. After a negotiation with the platform
sales department, they agreed to a fair contract between the parties. The IT team of the university sent the details of
the authentication gateway to S\&C dev team: the platform now allows students and pre-designed university personnel to
login using the organization credentials.

\par{\textbf{Scenario 9: UN Deals with a Feedback}} Luca S., the project referent for S\&C in the school log onto the
platform using his PoliPo credentials. In the "My Internship" section he can see all ongoing and past internships
concerning only his students. In the "My Feedback" section he can see all the opened feedback by companies and
students. In this section he can reply to the message creator to further discuss the situation; a link here redirects
Luca on the proper internship in the "My Internship" section where he can suspend the internship.
Moreover, if necessary, Luca can prevent his students from seeing and applying for internship from a specific company
if he feels that these enterprises are mistreating his students. All blocked companies and the contracts between S\&C
and the university are available in the "My Contracts" section.
