\chapter{Specific Requirements}
\label{chap:specific-requirements}

\par This chapter provides detailed specifications for the requirements previously mentioned that may require
additional clarification for the development team's implementation.

\section{External Interface Requirements}
\label{sec:external-interface-requirements}

\subsection{User Interfaces}
\label{subsec:user-interfaces}

\par The user interface of S\&C is implemented as a web-based application, making it accessible through standard web
browsers. No specialized software installation is required - users only need a web browser and an internet connection
to access all platform features.

\subsection{Hardware Interfaces}
\label{subsec:hardware-interfaces}

\par S\&C – being a web application – will be available on all devices, connected to the internet, capable of running a
modern browser. Users can use S\&C on laptops, desktops, smartphones, tablets, ...

\subsection{Software Interfaces}
\label{subsec:software-interfaces}

\par The system will primarily function as a standalone application. The only external dependency is the SSO portals of
the various UN organizations that have requested enrollment in S\&C, which will provide access to UN personnel and STs.

\subsection{Communication Interfaces}
\label{subsec:communication-interfaces}

\par The system primarily relies on HTTPS for secure communication. This includes communication between users and the
frontend, as well as between the frontend and backend, and between the backend and the various SSO portals.

\par The SMTP protocol is also used to send notifications to the user's email address when necessary.

